Generation of Variation and Mean Fitness Increase: \\ Necessity is the Mother of Genetic Invention

### 2017-12-01 ms.tex
remove hats after eq 34

Note that if the modifier has the same effect on all types,
then we can substitute $C = \mu I$ (with $\mu > 0$) in Eq.~\ref{eq:model_equilibrium}, and proceeding as in Eq.~\ref{eq:mfp_K}, we find a relationship previously described by~\citet[eq.~24]{Hermisson2002},
\begin{equation}\label{eq:mutational_loss}
\frac{\partial \hat{\bar{w}}}{\partial \mu} = 
-\frac{1}{\mu}\left(\sum_{k=1}^{n} \hat u_k \hat v_k w_k - \hat{\bar{w}} \right) = -\frac{1}{\mu} G,
\end{equation}
where $\hat u_k$ and $\hat v_k$ are computed at the equilibrium associated with $\mu$ and $\hat{\bar{w}}$ is the mean fitness at that equilibrium.
$G$, the difference between the \emph{ancestral mean fitness} $(\sum_{k=1}^{n} \hat u_k \hat v_k w_k)$ and the \emph{stable population mean fitness} $(\hat{\bar{w}})$ when $C_k=\mu$, is  called the \emph{mutational loss}~\citep{Hermisson2002}.

>>>>

Note that if the modifier has the same effect on all types,
then we can substitute $C = \mu I$ (with $\mu > 0$) in Eq.~\ref{eq:model_equilibrium}, and proceeding as in Eq.~\ref{eq:mfp_K}, we find a relationship previously described by~\citet[eq.~24]{Hermisson2002},
\begin{equation}\label{eq:mutational_loss}
\frac{\partial {\bar{w}}}{\partial \mu} = 
-\frac{1}{\mu}\left(\sum_{k=1}^{n}  u_k  v_k w_k - {\bar{w}} \right) = -\frac{1}{\mu} G,
\end{equation}
where $u_k,v_k$ are computed at the equilibrium associated with $\mu$ and $\bar w$ is the mean fitness at that equilibrium. $G$ is the difference between the \emph{ancestral mean fitness} $(\sum_{k=1}^{n}  u_k  v_k w_k)$ and the \emph{stable population mean fitness} $({\bar{w}})$ when $C_k=\mu$, is  called the \emph{mutational loss}~\citep{Hermisson2002}.
